---
title: "Discrete Distribution and Continuous Distribution"
output: html_notebook
---


### Discrete Distribution
#### Discrete Unifom Distribution PDF
```{r}
library(ggplot2)
ddu<-function(x,k) ifelse(x>=1 & x<=k & round(x)==x,1/k,0) 
dis_uniform_pdf <- function(k){
  x<-c(0:k)
  y<-sapply(x,ddu,k=k)
  df = data.frame(x=x,y=y)
  ggplot(df,aes(x=x,y=y))+geom_col(fill="darkblue")
}
dis_uniform_pdf(5)
```
##### Discrete Unifom Distribution CDF

```{r}
pdu<-function(x,k) ifelse(x<1,0,ifelse(x<=k,floor(x)/k,1))
dis_uniform_pdf <- function(k){
  x<-c(0:k)
  y<-sapply(x,pdu,k=k)
  df = data.frame(x=x,y=y)
  ggplot(df,aes(x=x,y=y))+geom_col(fill="darkblue")
}
dis_uniform_pdf(5)
```

#### Binomial PDF
```{r}
plot_binom_pdf <- function(n,p){
  x <- c(0:n)
  binomial <- dbinom(x,n,p)
  df = data.frame(x=x,y=binomial)
  ggplot(df,aes(x=x,y=y))+geom_col(fill="darkblue")
}
plot_binom_pdf(40,0.05)
```
##### Binomial CDF
```{r}
plot_binom_cdf <- function(n,p){
  x <- c(0:n)
  binomial <- pbinom(x,n,p)
  df = data.frame(x=x,y=binomial)
  ggplot(df,aes(x=x,y=y))+geom_col(fill="darkblue")
}
plot_binom_cdf(40,0.05)
```

#### Bernoulli PDF
```{r}
plot_bio_pdf <- function(p){
  plot_binom_pdf(1,p)
}
plot_bio_pdf(0.2)
```
##### Bernoulli CDF
```{r}
plot_bio_pdf <- function(p){
  plot_binom_cdf(1,p)
}
plot_bio_pdf(0.2)
```

#### HyperGeometric PDF
```{r}
plot_hyper_pdf <- function(N,M,n){
  x <- c(0:N)
  hyper <- dhyper(x,N,M,n)
  df = data.frame(x=x,y=hyper)
  ggplot(df,aes(x=x,y=y))+geom_col(fill="darkblue")
}
plot_hyper_pdf(20,30,10)
```
##### HyperGeometric CDF
```{r}
plot_hyper_cdf <- function(N,M,n){
  x <- c(0:N)
  hyper <- phyper(x,N,M,n)
  df = data.frame(x=x,y=hyper)
  ggplot(df,aes(x=x,y=y))+geom_col(fill="darkblue")
}
plot_hyper_cdf(10,30,10)
```

##### Poisson pdf
```{r}
plot_poi_pdf <- function(N,lambda){
  x <- c(0:N)
  poi <- dpois(x,lambda)
  df = data.frame(x=x,y=poi)
  ggplot(df,aes(x=x,y=y))+geom_col(fill="darkblue")
}
plot_poi_pdf(40,3)
```

##### Poisson cdf
```{r}
plot_poi_cdf <- function(N,lambda){
  x <- c(0:N)
  poi <- ppois(x,lambda)
  df = data.frame(x=x,y=poi)
  ggplot(df,aes(x=x,y=y))+geom_col(fill="darkblue")
}
plot_poi_cdf(20,3)
```
#### Negative Binomial pdf
```{r}
plot_negBin_pdf <- function(N,r,p){
  x <- c(0:N)
  y <- dnbinom(x,r,p)
  df = data.frame(x=x,y=y)
  ggplot(df,aes(x=x,y=y))+geom_col(fill="darkblue")
}
plot_negBin_pdf(100, 10,0.3)
```
##### Negative Binomial cdf
```{r}
plot_negBin_cdf <- function(N,r,p){
  x <- c(0:N)
  y <- pnbinom(x,r,p)
  df = data.frame(x=x,y=y)
  ggplot(df,aes(x=x,y=y))+geom_col(fill="darkblue")
}
plot_negBin_cdf(50, 10,0.3)
```



### Continuous Distribution
#### Continuous Uniform Distribution PDF
```{r}
dis_uniform_pdf <- function(start,end){
  x<-seq(start-1,end+1,by = 0.001)
  y<-dunif(x,start,end)
  df = data.frame(x=x,y=y)
  ggplot(df,aes(x=x,y=y))+geom_line(color = "darkred")
}
dis_uniform_pdf(5,6)
```
##### Continuous Uniform Distribution CDF
```{r}
dis_uniform_pdf <- function(start,end){
  x<-seq(start-1,end+1,by = 0.001)
  y<-punif(x,start,end)
  df = data.frame(x=x,y=y)
  ggplot(df,aes(x=x,y=y))+geom_line(color = "darkred")
}
dis_uniform_pdf(5,6)
```

#### Normal Distribution PDF
```{r}
# x0 is start of the interval and x1 is end of the interval
plot_norm_pdf <- function(x0,x1,m,v){
  x<-seq(x0,x1,by = 0.001)
  y<-dnorm(x,m,v)
  df = data.frame(x=x,y=y)
  ggplot(df,aes(x=x,y=y))+geom_line(color = "darkred")
}
plot_norm_pdf(0,15,5,2)
```

##### Normal Distribution CDF
```{r}
# x0 is start of the interval and x1 is end of the interval
plot_norm_cdf <- function(x0,x1,m,v){
  x<-seq(x0,x1,by = 0.001)
  y<-pnorm(x,m,v)
  df = data.frame(x=x,y=y)
  ggplot(df,aes(x=x,y=y))+geom_line(color = "darkred")
}
plot_norm_cdf(0,15,5,2)
```
#### Gamma Distribution PDF
```{r}
# x0 is start of the interval and x1 is end of the interval
plot_gamma_pdf <- function(x0,x1,a,b){
  x<-seq(x0,x1,by = 0.001)
  y<-dgamma(x,a,b)
  df = data.frame(x=x,y=y)
  ggplot(df,aes(x=x,y=y))+geom_line(color = "darkred")
}
plot_gamma_pdf (0,15,5,2)
```

##### Gamma Distribution CDF
```{r}
# x0 is start of the interval and x1 is end of the interval
plot_gamma_cdf <- function(x0,x1,a,b){
  x<-seq(x0,x1,by = 0.001)
  y<-pgamma(x,a,b)
  df = data.frame(x=x,y=y)
  ggplot(df,aes(x=x,y=y))+geom_line(color = "darkred")
}
plot_gamma_cdf (-1,15,5,2)
```

#### Exponential Distribution PDF
```{r}
# x0 is start of the interval and x1 is end of the interval
plot_exp_pdf <- function(x0,x1,a){
  x<-seq(x0,x1,by = 0.001)
  y<-dexp(x,a)
  df = data.frame(x=x,y=y)
  ggplot(df,aes(x=x,y=y))+geom_line(color = "darkred")
}
plot_exp_pdf (0,5,3)
```
#### Exponential Distribution CDF
```{r}
# x0 is start of the interval and x1 is end of the interval
plot_exp_cdf <- function(x0,x1,a){
  x<-seq(x0,x1,by = 0.001)
  y<-pexp(x,a)
  df = data.frame(x=x,y=y)
  ggplot(df,aes(x=x,y=y))+geom_line(color = "darkred")
}
plot_exp_cdf (0,5,3)
```

#### Beta Distribution PDF
```{r}
# x0 is start of the interval and x1 is end of the interval
plot_beta_pdf <- function(x0,x1,a,b){
  x<-seq(x0,x1,by = 0.001)
  y<-dbeta(x,a,b)
  df = data.frame(x=x,y=y)
  ggplot(df,aes(x=x,y=y))+geom_line(color = "darkred")
}
plot_beta_pdf (0,5,3,5)
```

#### Beta Distribution CDF
```{r}
# x0 is start of the interval and x1 is end of the interval
plot_beta_pdf <- function(x0,x1,a,b){
  x<-seq(x0,x1,by = 0.001)
  y<-pbeta(x,a,b)
  df = data.frame(x=x,y=y)
  ggplot(df,aes(x=x,y=y))+geom_line(color = "darkred")
}
plot_beta_pdf (0,2,3,5)
```

