---
title: "Experiment and Relative Frequency"
output: html_notebook
---
#### Experiment
##### Coin Toss (fair)
```{r}
library(ggplot2)
coin <- c('heads','tails')
coin_toss <- function(){
return(sample(x=coin,size = 1,replace = FALSE, prob = c(0.5,0.5)))
}
table(replicate(10000,coin_toss()))

```

##### Relative Frequency (target is head/tail)
```{r}
coin_target<- function(target){
  result<- replicate(1,coin_toss())
  return(sum(result == target))
}
coin_toss_frequency <- function(target){
  x <- 1:10000
  y <- c()
  coin_exp<- replicate(10000,coin_target(target))
  for(k in x){
    y <- c(y,mean(coin_exp[1:k]))
  }
  frame <- data.frame("Number of Trials" =x,"Probability"=y)
ggplot(data = frame, aes(x=x,y=y))+geom_line(color="dark blue")+ ggtitle(target) +
  xlab("Number of Trials") + ylab("Probability")
}
coin_toss_frequency("heads")
coin_toss_frequency("tails")
```

##### 5 Coin Toss Count Number of Heads
```{r}
coin_head <- function(){
result <- sample(x=coin,size = 5,replace = TRUE, prob = c(0.5,0.5))
return(sum(result=="heads"))
}
table(replicate(10000,coin_head()))
```
##### Relative Frequency (Target is the number you want to track)
```{r}
count_head_target<- function(target){
  result<- coin_head()
  return(sum(result == target))
}
count_head_frequency <- function(target){
  x <- 1:20000
  y <- c()
  coin_exp<- replicate(20000,count_head_target(target))
  for(k in x){
    y <- c(y,mean(coin_exp[1:k]))
  }
  frame <- data.frame("Number of Trials" =x,"Probability"=y)
ggplot(data = frame, aes(x=x,y=y))+geom_line(color="dark blue")+ ggtitle(target) +
  xlab("Number of Trials") + ylab("Probability")
}
count_head_frequency(0)
count_head_frequency(3)
```

##### 5 Coin tosses, check if 3rd toss is a H
```{r}
coin_3_H <- function(){
  result <- sample(x=coin,size = 5,replace = TRUE, prob = c(0.5,0.5))
  if (result[2]== "heads"){
    return(FALSE)
  }else{
    return(TRUE)
  }
}
table(replicate(10000,coin_3_H()))
```
##### Relative Frequency(Target is eithr TRUE or FALSE)
```{r}
check_3_target<- function(target){
  result<- coin_3_H()
  return(sum(result == target))
}
check_3_frequency <- function(target){
  x <- 1:20000
  y <- c()
  coin_exp<- replicate(20000,check_3_target(target))
  for(k in x){
    y <- c(y,mean(coin_exp[1:k]))
  }
  frame <- data.frame("Number of Trials" =x,"Probability"=y)
ggplot(data = frame, aes(x=x,y=y))+geom_line(color="dark blue")+ ggtitle(target) +
  xlab("Number of Trials") + ylab("Probability")
}
check_3_frequency(TRUE)
check_3_frequency(FALSE)
```

##### Toss coin until two heads
```{r}
until_two_heads <- function(){
  result <- sample(x=coin,size = 1,replace = TRUE, prob = c(0.5,0.5))
  while(sum(result=="heads")!= 2){
    result = append(result, sample(x=coin,size = 1,replace = TRUE, prob = c(0.5,0.5)))
  }
  return(length(result))
}
table(replicate(10000,until_two_heads()))
```
##### Relative Frequency (Target is any positive number greater or equal to 2)
```{r}
how_many_two_heads<- function(target){
  result<- until_two_heads()
  return(sum(result == target))
}
how_many_frequency <- function(target){
  x_max <- (20000 * target/2)
  x <- 1:x_max
  y <- c()
  coin_exp<- replicate(x_max,how_many_two_heads(target))
  for(k in x){
    y <- c(y,mean(coin_exp[1:k]))
  }
  frame <- data.frame("Number of Trials" =x,"Probability"=y)
ggplot(data = frame, aes(x=x,y=y))+geom_line(color="dark blue")+ ggtitle(target) +
  xlab("Number of Trials") + ylab("Probability")
}
how_many_frequency(2)
how_many_frequency(4)
```

##### Toss coin followed by a fair dice
```{r}
coin_fair <- function(){
  coin <- sample(x=coin,size = 1,replace = TRUE, prob = c(0.5,0.5))
  dice <- sample(x=c(1,2,3,4,5,6), size =1, replace = TRUE, prob = c(1/6,1/6,1/6,1/6,1/6,1/6))
  result <- append(coin,dice)
  return(result)
}
table(replicate(10000,coin_fair()))

```
##### Relative Frequency Of Numbers of Dice(Target is 1 to 6 )
```{r}
fair_target<- function(target){
  result<- coin_fair()
  return(sum(result== target))
}
fair_frequency <- function(target){
  x <- 1:20000
  y <- c()
  coin_exp<- replicate(20000,fair_target(target))
  for(k in x){
    y <- c(y,mean(coin_exp[1:k]))
  }
  frame <- data.frame("Number of Trials" =x,"Probability"=y)
ggplot(data = frame, aes(x=x,y=y))+geom_line(color="dark blue")+ ggtitle(target) +
  xlab("Number of Trials") + ylab("Probability")
}
fair_frequency(1)
fair_frequency(5)
```
##### Toss coin, if head roll fair dice, else roll unfiar coin (0.5 for a 6, rest 0.1 )
```{r}
coin_unfair <- function(){
  coin_result <- sample(x=coin,size = 1,replace = TRUE, prob = c(0.5,0.5))
  dice <- 0
  if (sum(coin_result=="heads")!= 1){
    dice <- sample(x=c(1,2,3,4,5,6), size =1, replace = TRUE, prob = c(0.1,0.1,0.1,0.1,0.1,0.5))
  }else{
    dice <- sample(x=c(1,2,3,4,5,6), size =1, replace = TRUE, prob = c(1/6,1/6,1/6,1/6,1/6,1/6))
  }
  return(append(coin_result, dice))
}
table(replicate(10000,coin_unfair()))
```
##### Relative Frequency Of Numbers of Dice(Target is 1 to 6 )
```{r}
unfair_target<- function(target){
  result<- coin_unfair()
  return(sum(result== target))
}
unfair_frequency <- function(target){
  x <- 1:20000
  y <- c()
  coin_exp<- replicate(20000,unfair_target(target))
  for(k in x){
    y <- c(y,mean(coin_exp[1:k]))
  }
  frame <- data.frame("Number of Trials" =x,"Probability"=y)
ggplot(data = frame, aes(x=x,y=y))+geom_line(color="dark blue")+ ggtitle(target) +
  xlab("Number of Trials") + ylab("Probability")
}
fair_frequency(2)
fair_frequency(6)
```