---
title: "Random Samples"
output: html_notebook
---

Sample Max
```{r}

sample_max<- function(sample){
  return (max(sample))
}
```

Sample Min
```{r}
sample_min<- function(sample){
  return (min(sample))
}
```

Sample Mean
```{r}
sample_mean<- function(sample){
  return (mean(sample))
}
```

Sample Variance
```{r}
sample_variance<- function(sample){
  return (var(sample))
}
```

Sample Mean Inverse
```{r}
sample_mean_inverse<- function(sample){
  mean_sample <- mean(sample)
  if (mean_sample == 0){
    return(0)
  }
  return(1/(mean_sample))
}
```

Sample Mean Squared
```{r}
sample_mean_squared<- function(sample){
  mean_sample <- mean(sample)
  return(mean_sample*mean_sample)
}
```

Sample 4th Largest Element
```{r}
sample_fourth_largest<- function(sample){
  fourth_largest <-sort(sample, TRUE)[4]
  return(fourth_largest)
}
```

Normal Distribution($\mu=2,\sigma=4$,) Sample max Graph
```{r}
library(ggplot2)
value <- c()
n = 10000
for (i in 1:n){
sample <- rnorm(1000, 2, 4)
value[i] = sample_max(sample)
}
df <- data.frame(value = value)
ggplot(data = df,aes(value))+geom_histogram(bins=50)
```
Normal Distribution($\mu=2,\sigma=4$,) Sample Min Graph
```{r}
library(ggplot2)
value <- c()
n = 10000
for (i in 1:n){
sample <- rnorm(1000, 2, 4)
value[i] = sample_min(sample)
}
df <- data.frame(value = value)
ggplot(data = df,aes(value))+geom_histogram(bins=50)
```
Normal Distribution($\mu=2,\sigma=4$) 4th largest element Graph
```{r}
library(ggplot2)
value <- c()
n = 10000
for (i in 1:n){
sample <- rnorm(1000, 2, 4)
value[i] = sample_fourth_largest(sample)
}
df <- data.frame(value = value)
ggplot(data = df,aes(value))+geom_histogram(bins=20)
```
Normal Distribution($\mu=2,\sigma=4$,) Sample Mean Graph
```{r}
library(ggplot2)
mean_value <- c()
n = 10000
for (i in 1:n){
  sample <- rnorm(1000, 2, 4)
mean_value[i] = sample_mean(sample)
}
df <- data.frame(meanValue = mean_value)
ggplot(data = df)+geom_histogram(mapping = aes(x= mean_value,y=after_stat(density)),bins=20, fill = "steelblue")+stat_function(fun = dnorm, args=list(mean = 2, sd = 4/sqrt(1000)))
```

Normal Distribution($\mu=2,\sigma=4$,) Sample Variance Graph
```{r}
variance_value <- c()
n = 10000
for (i in 1:n){
sample <- rnorm(1000, 2, 4)
variance_value[i] = sample_variance(sample)
}
df <- data.frame(variance = variance_value)
ggplot(data = df,aes(variance_value))+geom_histogram(bins=30)
```

Normal Distribution($\mu=2,\sigma=4$) Mean Inverse
```{r}
library(ggplot2)
value <- c()
n = 10000
for (i in 1:n){
sample <- rnorm(1000, 2, 4)
value[i] = sample_mean_inverse(sample)
}
df <- data.frame(value = value)
ggplot(data = df,aes(value))+geom_histogram(bins=20)
```
Normal Distribution($\mu=2,\sigma=4$) Mean Squared
```{r}
library(ggplot2)
value <- c()
n = 10000
for (i in 1:n){
sample <- rnorm(1000, 2, 4)
value[i] = sample_mean_squared(sample)
}
df <- data.frame(value = value)
ggplot(data = df,aes(value))+geom_histogram(bins=20)
```