---
title: "R Manual"
output: html_notebook
---
### Variable Assignment 

#### Variables
```{r}
x <- 2
y <- 3
z <- TRUE
x
y
z
```

#### Vector
```{r}
x <- c(1, 2, 3, 4, 5)
x
y <- c(0:3)
y
```

#### Sequence
```{r}
seq1 <- seq(1, 10)
seq2 <- seq(1, 10, by = 2)
seq3 <- seq(1, 10, by = 0.5)
seq1
seq2
seq3
```


### Loops And Conditional Statements

#### Loops
```{r}
x = 0
while (x!= 5){
  print(x)
  x = x + 1
}
print("While loop end")

```
```{r}
x <- c(2,5,3,9,8)
count <- 0
for (val in x) {
  print(val)
}
print("For Loop End")
```
#### If-Else
```{r}
x <- -5
if(x > 0){
  print("Non-negative number")
} else {
  print("Negative number")
}
```
### Functions

#### Build-in Functions
```{r}
x <- seq(0, 10)
squared <- x**2
cubed <- x**3
square_root <- x**(1/2)
sinx <- sin(x)
squared
cubed 
square_root
sinx
```

#### Self-Defined Functions
##### Step function
```{r}
# Function that takes a x valuewill return y value. 
#If 0<=x<=5 return 3, if 5<x<=6 return 5.5, if 6<x<10 
#return 7.5 Otherwise return 0  
step_fun <- function(x){
  result <- 0
  if (0<=x & x<=5){
    result <- 3
  }
  if (5<x& x<=6){
    result <-5.5
  }
  if (6<x&x<10){
    result <- 7.5
  }
  return(result)
}
x <- seq(1, 10)
step <- sapply(x,step_fun)
step
```
##### Functions as parts
```{r}
#Functions that takes a value x
# return x^2 if x<0. else x**(1/2)
part_func <- function(x){
  if (x<0){
    return(x**2)
  }
  if (x>=0){
    return(x**(1/2))
  }
}
x <- c(-5: 5)
part <- sapply(x,part_func)
part
```
##### Functions calculate the sum of first n numbers in a vector(sequence)
```{r}
nSum <- function(x,n){
  i = 1
  sum = 0
  for (val in x){
    if (i<=n){
      sum = sum + val
      i = i + 1
    }
  }
  return(sum)
}
x <- seq(1, 10)
result <- nSum(x,5)
result
```

### Plot Funcions Using ggplot
#### Create Dataframe
```{r}
x<-seq(-5,5, by= .1)
y <- sapply(x,part_func)
df = data.frame(x=x,y=y)
df
```
#### ggplot
```{r}
#install.packages("ggplot2")
library(ggplot2)
ggplot(df,aes(x=x,y=y))+geom_line()
```
##### Plot multiple graphs in one graphs with different colors 
```{r}
y2 = x**4
df2 = data.frame(x=x,y=y,y2=y2)
ggplot(df2,aes(x=x,y=y))+geom_line(color="red")+geom_line(y=y2,color="blue")
```
#### Function that outputs a plot
```{r}
# Functions that takes x and y vectors with same length
# and return a graph.
plot_func<- function(x,y){
  df = data.frame(x=x,y=y)
  ggplot(df,aes(x=x,y=y))+geom_line(color="red")
}
plot_func(x,y2)
```

